%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Authored by Nitin Prakash 
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{tgbonum}

\name{Nitin Prakash} % Your name
\address{110 - 30 Carabob Court \\ Scarborough, ON M1T3N2} % Your address
\address{(647)~$\cdot$~822~$\cdot$~0469 \\ nitinprakash@hotmail.com} % Your phone number and email

\begin{document}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Sunlife Financial}{June 2016 - November 2016}{Application Developer II}{Toronto, CA}
\item Developed, designed and maintained applications and enhancements with a primarily focus on back-end development using .NET, VB, C\# and SQL.
\item Developed ETL jobs with Informatica Designer and worked with various transformations including Router, Sorter, Lookup, and Expression transformation. 
\item Implemented new applications and enhancements to production by following existing Change Management processes and performing code deployment to production. 
\item Authored comprehensive design documents by working closely with Business Analysts and end users to understand and implement complex business requirements. 

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Sunlife Financial}{June 2014 - June 2016}{Application Developer}{Toronto, CA}
\item Developed and maintained existing applications, enhancements and business reports primarily using .NET, VB, C\#, SQL and SAP Crystal Reports.  
\item Provided production support by investigating and fixing production bugs during warranty phase and on-call support shifts.  


\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{CIBC}{April 2013 - August 2013}{Developer - Coop}{Toronto, CA}
\item Worked as a Development Integrated Test (DIT) analyst to perform DIT tests on new services.
\item Created test cases and planned testing of new service components, intakes and change requests by studying requirements, use case and detail design documents. Reported defects after testing and assigned variances to the respective developers.

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages \& Frameworks & VB/C\#.NET, Angular 2, Typescript, HTML, CSS, Java, C/C++ \\ 
Database \& ETL & SQL Server, Oracle, Informatica Power Center \\
Tools & Visual Studio, Informatica Designer, \\ & Dimensions CM, SAP Crystal Reports, Visual Studio Code,\\ &  Eclipse, Git Hub, Lotus Notes, ZEKE, Charm.
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor Of Technology, Software Development} \hfill {\em 2010 - 2014} \\ 
Seneca College, Toronto CA \\
% Minor in Linguistics \smallskip \\
% Member of Eta Kappa Nu \\
% Member of Upsilon Pi Epsilon \\
% Overall GPA: 5.678

\end{rSection}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Side Projects}

{\bf Angular 2 based project 1} \\
{\bf Angular 2 based project 2}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
